Actuator line modeling of vertical-axis turbines

### 2016-05-12 paper.tex
Fix U_in in figure caption

    \caption{Vector diagram of velocity and forcing on a cross-flow turbine
        blade element. Note that the free stream velocity $U_\infty$ is oriented
        from top to bottom (identical to $U_in$ for purely geometric calculations),
        the blade chord (dash-dotted line) is coincident with the tangential
        velocity (i.e., zero preset pitch, which would offset the geometric angle of
        attack $\alpha$), and the drag vector is magnified by a factor of two
        (approximately, relative to the lift vector) to enhance visibility.}

>>>>

    \caption{Vector diagram of velocity and forcing on a cross-flow turbine
    blade element. Note that the free stream velocity $U_\infty$ is oriented
    from top to bottom (identical to $U_{\mathrm{in}}$ for purely geometric
    calculations), the blade chord (dash-dotted line) is coincident with the
    tangential velocity (i.e., zero preset pitch, which would offset the
    geometric angle of attack $\alpha$), and the drag vector is magnified by a
    factor of two (approximately, relative to the lift vector) to enhance
    visibility.}
